Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-15 paper/conclusion.tex
Worsdmithing in the Conclusion section

The DARPA CASE program is creating tools for systems engineers to integrate cyber-vulnerability analysis and mitigation. The resulting BriefCASE tool suite includes analysis tools for generating cyber requirements, cyber resiliency tools for addressing the requirements, verification tools for ensuring design correctness, and synthesis tools for generating provably correct code. Several of the BriefCASE transforms (filter, monitor, gate) insert components into the model whose behavior can be formally specified in the AGREE language.
The SPLAT tool can then automatically generate CakeML implementations for these components, along with proofs of correctness for assurance that the implementation satisfies the specification.

@@

We are currently in the process of applying BriefCASE to the design of an application using the Collins Common Avionics Architecture System (CAAS)~\cite{caas} on the CH-47.  Other ongoing work includes adding support for uninterpreted functions, mechanizing the synthesis proof in HOL4 and lifting the proof results to infinite streams.

>>>>

The DARPA CASE program is creating tools for systems engineers to integrate cyber-vulnerability analysis and mitigation into their development workflow. The resulting BriefCASE tool suite includes analysis tools for generating cyber requirements, cyber resiliency tools for addressing the requirements, verification tools for ensuring design correctness, and synthesis tools for generating provably correct code. Several of the BriefCASE transforms (filter, monitor, gate) insert components into the model whose behavior can be formally specified using the AGREE language.
The SPLAT tool can then automatically generate CakeML implementations for these components, along with proofs of correctness for assurance that the implementation satisfies the specification.

@@

We are currently in the process of applying BriefCASE to the design of an application using the Collins Common Avionics Architecture System (CAAS)~\cite{caas} on the CH-47F Chinook helicopter as part of the DARPA CASE program.  Other ongoing work includes adding support for uninterpreted functions, mechanizing the synthesis proof in HOL4 and lifting the proof results to infinite streams.
